Asymmetric relationships and their effects on coexistence

### 2023-05-26 paper/Paper.Rnw
trivial

#place R code here for loading in necessary variables from Results
res_loc <- "../results_numeric/"
#fig2 <- readRDS(file=paste0(res_loc,"fig2data.RDS"))
M <- readRDS(file=paste0(res_loc,"M.RDS"))
se3 <- readRDS(file=paste0(res_loc,"fig3maxse.RDS"))
se4 <- readRDS(file=paste0(res_loc,"fig4maxse.RDS"))
#se5 <- readRDS(file=paste0(res_loc, "fig5maxse.RDS"))
#se6 <- readRDS(file=paste0(res_loc, "fig6maxse.RDS"))
@

@@

\noindent Figure 4. ATA effects and ATA rescue in the diatom system. 
The contribution of ATAs to the GWR of \emph{F. crotonensis}
in the diatom system of \cite{Descamps_2005} was often meaningfully large compared to 
other components of the MCT decomposition (a-c). Panels a-c show GWR and the decomposition of
GWR provided by the extended MCT, equation (\ref{eq:full_decomp}). 
For each panel, 
two of the three parameters defining the temperature oscillation (the amplitude, $a$; period, $P$; 
and mean, $\theta_0$; see Methods) were fixed at the values used by 
\cite{Descamps_2005} ($a=6^\circ$C, $P=60$d, $\theta_0=18^\circ$C), and 
GWR and components of the MCT decomposition
were plotted against the third parameter. The original values of the varying parameters 
are indicated by vertical dotted lines. 
ATA contributions ($\Delta_i^{[EC]}$)
had magnitude comparable to other components, 
indicating that ATAs can contribute meaningfully
to coexistence in this system. In some instances, the GWR line falls 
between the ATA line
and the horizontal axis, indicating that, for those parameter values, ATA rescue occurs. 
Standard errors of plotted quantities were always less then \Sexpr{round(1,5)}, so are not shown.
Panels d-f show bivariate plots (Methods) for which the third parameter was 
fixed at the values used by \cite{Descamps_2005}. ATAs are again often an important factor helping
determine coexistence or exclusion, and ATA rescue happened for an appreciable fraction of the
explored parameter space.
For the parameters we considered, GWR of the other diatom species in the system, 
\emph{C. pseudostelligera}, was always positive both including and
excluding the effects of ATAs, so GWR for \emph{F. crotonensis}, decomposed here, is a 
sufficient coexistence metric.

>>>>

#place R code here for loading in necessary variables from Results
res_loc <- "../results_numeric/"
#fig2 <- readRDS(file=paste0(res_loc,"fig2data.RDS"))
M <- readRDS(file=paste0(res_loc,"M.RDS"))
se3 <- readRDS(file=paste0(res_loc,"fig3maxse.RDS"))
se4 <- readRDS(file=paste0(res_loc,"fig4maxse.RDS"))
se5 <- 1 #readRDS(file=paste0(res_loc, "fig5maxse.RDS"))
#se6 <- readRDS(file=paste0(res_loc, "fig6maxse.RDS"))
@

@@

\noindent Figure 4. ATA effects and ATA rescue in the diatom system. 
The contribution of ATAs to the GWR of \emph{F. crotonensis}
in the diatom system of \cite{Descamps_2005} was often meaningfully large compared to 
other components of the MCT decomposition (a-c). Panels a-c show GWR and the decomposition of
GWR provided by the extended MCT, equation (\ref{eq:full_decomp}). 
For each panel, 
two of the three parameters defining the temperature oscillation (the amplitude, $a$; period, $P$; 
and mean, $\theta_0$; see Methods) were fixed at the values used by 
\cite{Descamps_2005} ($a=6^\circ$C, $P=60$d, $\theta_0=18^\circ$C), and 
GWR and components of the MCT decomposition
were plotted against the third parameter. The original values of the varying parameters 
are indicated by vertical dotted lines. 
ATA contributions ($\Delta_i^{[EC]}$)
had magnitude comparable to other components, 
indicating that ATAs can contribute meaningfully
to coexistence in this system. In some instances, the GWR line falls 
between the ATA line
and the horizontal axis, indicating that, for those parameter values, ATA rescue occurs. 
Standard errors of plotted quantities were always less then \Sexpr{round(se5,5)}, so are not shown.
Panels d-f show bivariate plots (Methods) for which the third parameter was 
fixed at the values used by \cite{Descamps_2005}. ATAs are again often an important factor helping
determine coexistence or exclusion, and ATA rescue happened for an appreciable fraction of the
explored parameter space.
For the parameters we considered, GWR of the other diatom species in the system, 
\emph{C. pseudostelligera}, was always positive both including and
excluding the effects of ATAs, so GWR for \emph{F. crotonensis}, decomposed here, is a 
sufficient coexistence metric.
